---
output:
  md_document:
    variant: gfm
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pathway

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis-CI Build Status](https://travis-ci.org/mdlincoln/pathway.svg?branch=master)](https://travis-ci.org/mdlincoln/pathway)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/mdlincoln/pathway?branch=master&svg=true)](https://ci.appveyor.com/project/mdlincoln/pathway)

pathway finds a pathway of observations between two points in a matrix.

## Installation

You can install pathway from GitHub with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mdlincoln/pathway")
```

## Example

```{r pathway}
library(pathway)

set.seed(34)
m <- matrix(rnorm(1000), nrow = 500, ncol = 2)
p1 <- 2L
p2 <- 11L
p <- pathway(m, p1, p2, n = 5)
p

plot_pathway(m, p)
```

It is also possible to place conditional restraints on the solution that `pathway` finds by using `navigate_` functions.
For example, `navigate_unique` will not revisit the same point along a path, and `navigate_ordered` will only look at points that occurr in later rows in the matrix.

```{r naviagte}
p_ordered <- pathway(m, 5, 380, n = 5, navigator = navigate_ordered)
plot_pathway(m, p_ordered)
```

To use your own predicate function, define a function that returns a vector of indices to search and call it with `navigator = navigate(f)`

```{r custom_navigate}
obs_types <- sample(c("setosa", "versicolor", "virginica"), 500, replace = TRUE)

# A custom predicate function must take the original matrix, the list of
# previously-selected pathway points, along with p1 and p2.
different_species <- function(x, pi, p1, p2, obs_types) {
  if (is.null(pi)) {
    search_space <- 1:nrow(x)
  } else {
    # Only search observations that do not have the same species as the immediately previous one.
    prev_type <- obs_types[tail(pi, 1)]
    search_space <- which(obs_types != prev_type)
  }
  
  # Don't forget to exclude p1 and p2
  setdiff(search_space, c(p1, p2))
}

p_species <- pathway(m, p1, p2, n = 8, navigator = navigate(different_species, obs_types))
obs_types[p_species$i]
```
